Extensions of entropy stable nodal discontinuous Galerkin schemes

### 2020-02-27 talks/WCCM2020/abstract.tex
adding more talks

% Type down your paper title
\title{Entropy stable discontinuous Galerkin methods using arbitrary bases and quadratures}

@@

\begin{abstract}
High order discontinuous Galerkin (DG) methods offer several advantages in the approximation of solutions of nonlinear conservation laws, such as improved accuracy and low numerical dispersion/dissipation.  However, these methods also tend to suffer from instability in practice, requiring filtering, limiting, or artificial dissipation to prevent solution blow up.  Provably stable DG methods based on summation-by-parts (SBP) operators and flux differencing address this inherent instability by ensuring that the solution satisfies a semi-discrete entropy inequality.

Under specific combinations of basis functions or quadratures, nodal DG methods can be interpreted within an SBP framework.  In this talk, we discuss how to construct discretely entropy stable discontinuous Galerkin methods for general choices of basis and quadrature using discrete $L^2$ projection operators and ``decoupled'' SBP operators.  Extensions to curvilinear meshes and implementational aspects on Graphics Processing Units will be also discussed.  
\end{abstract}

>>>>

% Type down your paper title
\title{Extensions of entropy stable nodal discontinuous Galerkin schemes}

@@

\begin{abstract}
High order discontinuous Galerkin (DG) methods provide improved accuracy and low numerical dispersion/dissipation for simulations of nonlinear conservation laws.  However, these methods also tend to suffer from instability in practice, requiring filtering, limiting, or artificial dissipation to prevent solution blow up.  \textit{Entropy stable} nodal DG methods based on summation-by-parts (SBP) operators and flux differencing address this instability by ensuring satisfaction of a semi-discrete entropy inequality.  In this talk, we will present extensions of entropy stable DG methods to more general nodal points, which provide improved accuracy on warped and non-conforming meshes.  
\end{abstract}
